---
title: "Product Pricing Algorithm"
author: "Ro Verma"
date: "August 2022"
output:
    github_document
params:
  interactive: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE,
    out.width = "100%")
```

```{r}
library(tidyverse)
library(tidyquant)
library(parsnip)
library(plotly)
```

```{r}
source("../00_scripts/separate_bikes_and_outlier_detection.R")
source("../00_scripts/plot_product_recommendation.R")
```

```{r}
bike_orderlines_tbl <- read_rds("../00_data/bike_orderlines.rds")
```

```{r}
models_tbl <- read_rds("../00_models/parsnip_models_tbl.rds")
```

## Problem Statement

Research and Development wants help to determine new product ideas and pricing using existing product line as a benchmark.

## Solution Summary

The following product gaps have been identified in the existing product line:

1.  Aluminum Over Mountain

2.  Aluminum Triathalon

A pricing model has been developed to predict the price of the new bike models based on the existing bikes to ensure that the new bike models are priced based on the price of existing bike models.

Price predicition for two new models:

1.  Trigger, Over Mountain with Aluminum Frame: \$2,231

2.  Slice, Triathalon with Aluminum Frame: \$2,438

### Bike List


```{r}
get_bike_features()
```

### Gaps

The visualization segments the full bicycle product line by category and frame material. This exposes two product gaps:

1.  New Aluminum line of bikes in the Over Mountain Category

2.  New Aluminum line of bikes in the Triathalon

```{r, out.height="600px"}
plot_bike_features(interactive = params$interactive)
```

\newpage

## Price Prediction

New product prediction for 2 new models:

1.  Trigger, Over Mountain with Aluminum Frame: \$2,231

2.  Slice, Triathalon with Aluminum Frame: \$2,438

```{r}
# CREATE NEW MODELS
new_over_mountain_trigger <- tibble(
    model = "Trigger Al 1",
    frame_material = "Aluminum",
    category_2 = "Over Mountain",
    model_base = "Trigger",
    model_tier = "Aluminum 1",
    black      = 0,
    hi_mod     = 0,
    team       = 0,
    red        = 0,
    ultegra    = 0,
    dura_ace   = 0,
    disc       = 0
) 

new_triathalon_slice_tbl <- tibble(
    model = "Slice Al 1",
    frame_material = "Aluminum",
    category_2 = "Triathalon",
    model_base = "Slice",
    model_tier = "Ultegra",
    black      = 0,
    hi_mod     = 0,
    team       = 0,
    red        = 0,
    ultegra    = 0,
    dura_ace   = 0,
    disc       = 0
) 

new_bikes_tbl <- bind_rows(new_over_mountain_trigger, 
                           new_triathalon_slice_tbl)
```

```{r}
# GET XGBOOST MODEL
model_07_xgboost <- models_tbl %>%
    filter(model_id %>% str_detect("XGBOOST")) %>%
    pull(model) %>%
    pluck(1)
```

```{r}
# OUTPUT PREDICTIONS IN A TABLE
model_07_xgboost %>%
    predict(new_bikes_tbl) %>%
    mutate(.pred = scales::dollar(.pred, accuracy = 1)) %>%
    bind_cols(new_bikes_tbl) %>%
    gather(key = "New Model Attribute", value = "value", -model, factor_key = T ) %>%
    spread(key = model, value = value)
```
