---
title: "Customer Segmentation"
author: "Ro Verma"
date: "August 2022"
output:
  pdf_document: default
  html_document:
    df_print: paged
    theme: flatly
params:
  interactive: FALSE
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE,
    out.width = "100%",
    fig.align = "center")
```

```{r}
library(tidyverse)
library(tidyquant)
library(broom)
library(umap)
library(ggrepel)
library(plotly)
```

```{r}
bike_orderlines_tbl <- read_rds("../00_data/bike_sales/data_wrangled/bike_orderlines.rds")
```

```{r}
source("../00_scripts/plot_customer_segmentation.R")
```
There are 4 clusters, which are related to customer segments and confirm that there customers have similar purchasing habits.  

## Problem Statement

Marketing would like to increase email campaign engagement by segmenting the customer-base using their buying habbits. 

## Solution Summary

The Data Science Team has identified 4 customer segments. The 4 customer segments were given descriptions based on the top products purchased by customer segments. 

1. Segment 1 Prefrences: Moutain Bikes, Above $3200

2. Segment 2 Prefrences: Road Bikes, Above $3200

3. Segment 3 Prefrences: Road Bikes, Below $3200

4. Segment 4 Prefrences: Both Road Bikes and Moutain Bikes, Below $3200


## Customer Preferences

### Heat Map

Our customers include 30 bike shops and many customers have purchasing preferences related to either mountain or road based on the proportion of bikes purchased by category_1 and category_2. 

```{r, fig.height=12}
# PLOT CUSTOMER HEAT MAP
plot_customer_heatmap(interactive = params$interactive)
```

### Customer Segmentation

The 4 customer segments were given descriptions based on the top products purchased by customer segments. 

1. Segment 1 Prefrences: Road Bikes 

2. Segment 2 Prefrences: Moutain Bikes 

3. Segment 3 Prefrences: Road Bikes

4. Segment 4 Prefrences: Both Road Bikes and Moutain Bikes

```{r, fig.height=5, fig.width=7}
# PLOT CUSTOMER SEGMENTS
plot_customer_segments(k = 4, seed = 123, interactive = params$interactive)
```


### Customer Preferences By Segment

```{r, fig.height=8}
# PLOT CUSTOMER BEHAVIOR
plot_customer_behavior_by_cluster(top_n_products = 10, k = 4, seed = 123, interactive = params$interactive)
```

